Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-12 tex/paper.tex
Add caption to figure 1

\begin{figure*}
  \includegraphics[width=\textwidth,height=8cm]{convtrans}
  \caption{This is a tiger.}
  \label{fig:convtrans}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth,height=8cm]{convtrans}
  \caption{Given an input image $I$ of size $w_{img} \times w_{img}$ with $c$ channels and $K$ kernels of size 
  $w_k \times w_k$ with $c$ channels, each region on which the kernel is applied can be flattened to form a 
  row of a matrix $I’$ of size $(w_{img} - w_k + 1)^2 \times c \cdot w_k^2$. The set of kernels can also be 
  flattened to form columns of a matrix $W$ of size $c \cdot w_k^2 \times K$. If we take the matrix product 
  of $I’$ and $W$, then the $i^\text{th}$ column of the resultant matrix is a flattened version of the image 
  convolved with the $i^\text{th}$ kernel. The matrix $W$ can be seen as the weights of a fully connected 
  network with $c \cdot w_k^2$ inputs and $K$ outputs. Thus, learning of the kernels is reduced to batch 
  learning of the weights of this fully connected network.
}
  \label{fig:convtrans}
\end{figure*}
